# Microreport

Nicoline Hansen: s203530

Ulrikke Furland: s204526

Anna Rasmussen: s215071

Mathilde Stenholt: s200047

Ida Lundberg: s215029

## Background

The data is patients with breast cancer. They are grouped into different categories; age, status after diagnosis, and gene expression levels (2905 different genes are measured).

## Aim

To investigate the correlation between expression level of the gene g1CNS507 and event after diagnosis.

## Load libraries

```{r}
library("tidyverse")
```

## Loading and cleaning data

```{r}
load("data/gravier.RData")

```

Cleaning the data and renaming:

```{r}
set.seed(676571)
cancer_data=mutate(as_tibble(pluck(gravier,"x")),y=pluck(gravier,"y"),pt_id=1:length(pluck(gravier, "y")),age=round(rnorm(length(pluck(gravier,"y")),mean=55,sd=10),1))
cancer_data=rename(cancer_data,event_label=y)
cancer_data$age_group=cut(cancer_data$age,breaks=seq(10,100,by=10))
cancer_data=relocate(cancer_data,c(pt_id,age,age_group,pt_id,event_label))
```

Viewing the data

```{r}
cancer_data
```

## Analysis

Making a plot to see the correlation between the g1CNS507 gene expression level and the event after diagnosis.

```{r}
ggplot(
  data = cancer_data,
  mapping = aes(x = g1CNS507, y = event_label, fill = event_label)) +
  geom_boxplot(alpha = 0.5) + 
  labs(title = "A prognostic DNA signature for T1T2 node-negative breast cancer patients", subtitle = "Labelling: good=no event, poor=early metastasis", x = "Expression level of g1CNS507 (log2 transformed)", y = "Event After Diagnosis", caption = "Data from gavier et. al. (2010)", fill = "Event label")
```

## Conclusion

More of the persons who have high expression of the gene g1CNS507 have no event after diagnosis compared to people who has lower expression of this gene.
