# Microreport

Nicoline Hansen: s203530

Ulrikke Furland: s204526

Anna Rasmussen: s215071

Mathilde Stenholt: s200047

Ida Lundberg: s215029

## Background

The data is patients with breast cancer. They are grouped into different categories; age, status after diagnosis, and gene expression levels (2905 different genes are measured).

## Aim

To investigate the correlation between expression level of the gene g1CNS507 and event after diagnosis.

## Load libraries

```{r}
library("tidyverse")
```

## Load data

```{r}
load(file = here("data/gravier.RData"))

```

```{r}
base_url <- "http://userweb.eng.gla.ac.uk/umer.ijaz/bioinformatics/ecological/"
raw_data_path <- "data/_raw/"

SPE <- read_csv(file = str_c(base_url, "SPE_pitlatrine.csv"))
write_csv(x = SPE,
          file = str_c(raw_data_path, "SPE_pitlatrine.csv"))

ENV <- read_csv(file = str_c(base_url, "ENV_pitlatrine.csv"))
write_csv(x = ENV,
          file = str_c(raw_data_path, "ENV_pitlatrine.csv"))


```

## Analysis

## Conclusion

More of the persons who have high expression of the gene g1CNS507 have no event after diagnosis compared to people who has lower expression of this gene.
